Technical Report

### 2017-11-03 fully-abstract-comp/technical-report.tex
made it more clear what can be both registers and numbers in the op. sem.
fleshed out some details in continuation relation

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

\begin{align*}
  \sem{\tjnz{r_1}{r_2}}(\Phi) = &       
                             \begin{cases}
                               \arraycolsep=0pt
                               \begin{array}[t]{rl}
                                 \Phi&\updReg{r_1}{w}\\
                                     &\updReg{\pcreg}{\Phi(r_1)}
                               \end{array}
                                               & w = \linCons{\Phi(r_1)} \tand \nonZero{\Phi(r_2)}\\
                               \updPcAddr{\Phi} & \totherwise
                             \end{cases}
\end{align*}

@@

\noindent\textbf{move}\\
\begin{align*}
  \sem{\tmove{r_1}{r_2}}(\Phi) = & 
                              \begin{cases}
                                \updPcAddr{\Phi\updReg{r_1}{r_2}} & r_2 \in \ints \\
                                \updPcAddr{\Phi\updReg{r_1}{\Phi(r_2)}} & \nonLinear{\Phi(r_2)}\\
                                \updPcAddr{\Phi\updReg{r_2}{0}\updReg{r_1}{\Phi(r_2)}} & \totherwise 
                              \end{cases}
\end{align*}
Notice that in the case where we are moving a linear capability and $r_1 = r_2$ the order of the updates matter.

@@

\noindent\textbf{cca}\\
\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r_1}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \updPcAddr{\Phi\updReg{r_1}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma} \tand \\
                                      c = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma + n}
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r_1}{c}}} &  
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi(r_2)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{r_3}} = &
                                      \begin{cases}
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\updReg{r_1}{c}
                                          \end{array} \right)
&
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \sourcecolor\left.
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{0}\\
                                                    &\updReg{r_1}{c}
                                          \end{array}\right)\right.
                                        &
                                        \sourcecolor\left.
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}
                                        \end{array}\right.
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

@@

\noindent\textbf{plus and minus}\\
\begin{align*}
  \sem{\tplus{r_0}{r_1}{r_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1+n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = r_i$ or $n_i = \Phi(r_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\begin{align*}
  \sem{\tminus{r_0}{r_1}{r_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1-n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = r_i$ or $n_i = \Phi(r_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

@@

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{c_\code,\sigma} \tand \\
                                       \Phi(r_2) = \sealed{c_\data,\sigma} \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma,\_) \tand \\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv},\aaddr_\stk) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

@@

  \sem{\tsplit{r_1}{r_2}{r_3}{r_4}} = &

@@

                                   \Phi(r_4) = n \tor r_4 = n \\

@@

\lau{19-10-2017: $\lrk$ may indicate that $\lre$ should really be a relation between a \src{source pc} and a pair of a target pc and stack pointer? Otherwise, what happens with the data part of the return pointer?}
\[
  \lrk(W) = \left\{ \npair{\left(\array{l}\src{\retptrd(\sigma,\_)},\\\src{\retptrc(\sigma,\_)},\\k_{d,T},k_{c,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} \text{ is a stack pointer with correct end and such with everything related to the source stack} \\
      k_{c,T} \text{ relates to the old pc on the stack}\\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall, W_\lrr, W_\lrm \ldotp  \\
      \qquad\npair[n']{\src{\retptrd(\sigma,\_)},\src{\retptrc(\sigma,\_)},k_{d,T},k_{c,T}} \in \lrp(W') \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rstk}{\opc,\stkptr{\dots}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rstk}{\dots,\dots})\endarray\right)}
      \in \lro(W' \oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
\]

>>>>

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

\begin{align*}
  \sem{\tjnz{r}{\rn}}(\Phi) = &       
                             \begin{cases}
                               \arraycolsep=0pt
                               \begin{array}[t]{rl}
                                 \Phi&\updReg{r}{w}\\
                                     &\updReg{\pcreg}{\Phi(r)}
                               \end{array}
                                               & w = \linCons{\Phi(r)} \tand \nonZero{\Phi(\rn)}\\
                               \updPcAddr{\Phi} & \totherwise
                             \end{cases}
\end{align*}

@@

\noindent\textbf{move}\\
\begin{align*}
  \sem{\tmove{r}{\rn}}(\Phi) = & 
                              \begin{cases}
                                \updPcAddr{\Phi\updReg{r}{\rn}} & \rn \in \ints \\
                                \updPcAddr{\Phi\updReg{\rn}{w}\updReg{r}{\Phi(\rn)}} & w = \linCons{\Phi(\rn)}
                              \end{cases}
\end{align*}
Notice that in the case where we are moving a linear capability and $r = \rn$ the order of the updates matter.

@@

\noindent\textbf{cca}\\
\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r}{\rn}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \updPcAddr{\Phi\updReg{r}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma} \tand \\
                                      c = \seal{\lin,\sigma_\baddr,\sigma_\eaddr,\sigma + n}
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r}{c}}} &  
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = \rn$ or $n = \Phi(\rn)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{\rn}} = &
                                      \begin{cases}
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\updReg{r_1}{c}
                                          \end{array} \right)
&
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \sourcecolor\left.
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{0}\\
                                                    &\updReg{r_1}{c}
                                          \end{array}\right)\right.
                                        &
                                        \sourcecolor\left.
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                          \text{either $n = \rn$ or $n = \Phi.\reg(\rn)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}
                                        \end{array}\right.
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

@@

\noindent\textbf{plus and minus}\\
\begin{align*}
  \sem{\tplus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1+n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = \rn_i$ or $n_i = \Phi(\rn_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

\begin{align*}
  \sem{\tminus{r_0}{\rn_1}{\rn_2}}(\Phi) = &
                                                  \begin{cases}
                                                    \updPcAddr{\Phi\updReg{r_0}{n_1-n_2}} &
                                                    \arraycolsep=0pt
                                                    \begin{array}[t]{l}
                                                      \text{if for $i \in \{1,2\}$}\\
                                                      \quad\text{$n_i = \rn_i$ or $n_i = \Phi(\rn_i)$}\\
                                                      \quad\text{and in either case $n_i \in \ints$}\\
                                                    \end{array}\\
                                                    \failed & \text{otherwise}
                                                  \end{cases}  
\end{align*}

@@

\noindent\textbf{xjmp}\\
\lau{22-09-2017: Can we allow the callee to return any stack pointer? At the moment, it is not possible to create an empty stack pointer which may be a saving grace. If we at some point change this, so you can split capabilities into empty ones, then we need to consider whether it is safe for callees to return empty stacks (I think it is okay as long as we always have some stack usage).}
\lau{28-09-2017: For now, the jump to a return pointer does the stack end point check. We could possibly move this to the proposed semantic condition as well.}
\begin{align*}
  \sem{\txjmp{r_1}{r_2}}(\Phi) = &
                                   \begin{cases}
                                     \arraycolsep=0pt
                                     \begin{array}[t]{rl}
                                       \Phi & \updReg{r_1}{w_1}\\
                                            & \updReg{r_2}{w_2}\\
                                            & \updReg{\pcreg}{c_\code}\\
                                            & \updReg{\rdata}{c_\data}
                                     \end{array} &
                                     \begin{array}[t]{l}
                                       \Phi(r_1) = \sealed{c_\code,\sigma} \tand \\
                                       \Phi(r_2) = \sealed{c_\data,\sigma} \tand \\
                                       \nonExec{c_\data} \tand \\
                                       w_1 = \linCons{\Phi(r_1)} \tand \\
                                       w_2 = \linCons{\Phi(r_2)}
                                     \end{array}
                                     \\&\\
                                     \sourcecolor\left.
                                       \arraycolsep=0pt
                                       \begin{array}[t]{rl}
                                         \Phi' & \updReg{r_2}{0} \\
                                               & \updReg{\pcreg}{\opc}\\
                                               & \updReg{\rdata}{0}\\
                                               & \updReg{\rstk}{c_\stk}
                                       \end{array}\right.&
                                     \sourcecolor\left.
                                       \begin{array}[t]{l}
                                         \Phi(r_1) = \retptrc(\sigma,\_) \tand \\
                                         \Phi(r_2) = \retptrd(\sigma,(\aaddr_\stk,\_)) \tand \\
                                         \Phi(\rstk) = \stkptr{\rw,\stkb,\eaddr_\stk,\_} \tand \\
                                         \Phi = (\mem,\reg,\stkf::\stk,\ms_\stk) \tand \\
                                         \stkf = (\opc,\ms_{\stk,\priv}) \tand \\
                                         \dom(\ms_{\stk,\priv}) = [\eaddr_\stk+1,\eaddr_{\stk,\priv}] \tand\\
                                         c_\stk = \stkptr{\rw,\stkb,\eaddr_{\stk,\priv},\aaddr_\stk} \tand\\
                                         \Phi' = (\mem,\reg,\stk,\ms_{\stk,\priv} \uplus \ms_\stk) 
                                       \end{array}\right.
                                     \\
                                     \failed & \totherwise
                                   \end{cases}
\end{align*}

@@

  \sem{\tsplit{r_1}{r_2}{r_3}{\rn_4}} = &

@@

                                   \Phi(\rn_4) = n \tor \rn_4 = n \\

@@

\lau{03-11-2017: TODO take a look at linearity of this definition - in paticular the recovered pc and stack pointer.}
\[
  \lrk(W) = \left\{ \npair{\left(\array{l}\src{\retptrd(\sigma,(\aaddr_d,\eaddr_d))},\\\src{\retptrc(\sigma,(\perm,\lin,\baddr_c,\eaddr_c,\aaddr_c))},\\k_{d,T},k_{c,T}\endarray\right)} \middle|
    \begin{array}{l}
      k_{d,T} = \sealed{\sigma,c_d} \wedge\\
      k_{c,T} = \sealed{\sigma,c_c} \wedge\\
      c_c = ((\perm,\lin),\baddr_c,\eaddr_c,\aaddr_c) \wedge\\
      c_d = ((\rw,\linear),\aaddr_d,\eaddr_d,\aaddr_d-1) \wedge\\
      \forall n' \leq n, W' \pubft W \ldotp \\
      \quad \forall, W_\lrr, W_\lrm \ldotp  \\
      \qquad\opc = c_c \wedge\\
      \qquad\dom(\ms_{\stk,f}) = [\aaddr_d,\eaddr_d] \wedge\\
      \qquad\npair[n']{\src{\retptrd(\sigma,\_)},\src{\retptrc(\sigma,\_)},k_{d,T},k_{c,T}} \in \lrp(W') \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk::(\opc,\ms_{\stk,f}),\ms_\stk}{\ms_T}}{W_\lrm} \wedge \\
      \qquad\dom(\ms_\stk) = [\baddr_\stk,\eaddr_\stk] \wedge \\
      \qquad\eaddr_\stk = \aaddr_d-1\\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{\left(\arraycolsep=0pt\array{l}\ms_S,\reg_S\updReg{\pcreg,\rstk}{\opc,\stkptr{\rw,\baddr_\stk,\eaddr_d,\_}},\\\stk, \ms_\stk \uplus \ms_{\stk,f}\endarray\right)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rstk}{\opc,((\rw,\lin),\baddr_\stk,\eaddr_d,\_)})\endarray\right)}
      \in \lro(W' \oplus W_\lrr \oplus W_\lrm)
    \end{array}
  \right\}
\]
